Dependently Typed Languages in Statix

### 2022-10-12 paper-evcs/oasics-v2021-sample-article.tex
Meeting result

\Copyright{Jane Open Access and Joan R. Public} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
\ccsdesc[100]{\textcolor{red}{Replace ccsdesc macro with valid one}}

@@

To type-check the base language, we need to store information about the names we have encountered. There are two different situations, names that we encounter that do not have a known value (only a type), such as function arguments, and names that do have a known value, such as let bindings.

   we need scope graphs. This section describes how scope graphs are used.

The scope graph only has a single type of edge, called \verb|P| (parent) edges. It also only has a single relation, called \verb|name|. This name stores a \verb|NameEntry|, which can be either a \verb|NameType|, which stores the type of a name, or a \verb|NameSubst|, which stores a substitution corresponding to a name.

@@

System F, which allows a term to depend on a type (also known as Type Polymorphism or Type-Generic Functions)  has been implemented before

The Calculus of Constructions is the top of the lambda cube. System F, which

>>>>

\Copyright{Jane Open Access and Joan R. Public} %TODO mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/
\begin{CCSXML}
    <ccs2012>
    <concept>
    <concept_id>10011007.10011006.10011039.10011311</concept_id>
    <concept_desc>Software and its engineering~Semantics</concept_desc>
    <concept_significance>500</concept_significance>
    </concept>
    <concept>
    <concept_id>10011007.10011006.10011008.10011009.10011012</concept_id>
    <concept_desc>Software and its engineering~Functional languages</concept_desc>
    <concept_significance>300</concept_significance>
    </concept>
    <concept>
    <concept_id>10011007.10011006.10011041</concept_id>
    <concept_desc>Software and its engineering~Compilers</concept_desc>
    <concept_significance>300</concept_significance>
    </concept>
    </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Semantics}
\ccsdesc[300]{Software and its engineering~Functional languages}
\ccsdesc[300]{Software and its engineering~Compilers}

@@

To type-check the base language, we need to store information about the names we have encountered. There are two different situations, names that we encounter that do not have a known value (only a type), such as function arguments, and names that do have a known value, such as let bindings.\footnote{In non-dependent languages there is no such distinction, but because we may need to value of a binding to compare types, this is needed in dependently typed languages.}

Both of these need to be stored in the scope graph. The scope graph only has a single type of edge, called \verb|P| (parent) edges. It also only has a single relation, called \verb|name|. This name stores a \verb|NameEntry|, which can be either a \verb|NameType|, which stores the type of a name, or a \verb|NameSubst|, which stores a substitution corresponding to a name.

@@

\subsection{}
